\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-03-17 archive.tex
regex

\usepackage[section]{placeins}
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
%\usepackage{hyperref}

@@

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{fit,bayesnet,calc,tikzmark}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{dsfont}
\usepackage{amsmath}

@@

@@

    \newcommand{\invention}[4]{
      \node(#1)[inner sep=1,anchor=south,text width=2.2cm,draw,rounded corners,align=center] at (#2) {
        \footnotesize #3
      };
      \node[anchor=north,align=center] at ([yshift=3.5pt]#1.south) {#4};
    }
    \newcommand{\vinvention}[4]{
      \invention{#1}{[yshift=-\verticalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\hinvention}[4]{
      \invention{#1}{[xshift=\horizontalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\exampleFunction}[2]{
      \includegraphics[width = 0.5cm]{#1}, \includegraphics[width = 0.5cm]{#2}
    }
    \newcommand{\task}[4]{
      \node[align=left,anchor=center](t#1) at (#2) {#3};
      \node[align=left](p#1) at ([yshift=-0.75cm]t#1.south) {#4};
    }
    \newcommand{\nextTask}[4]{
      \task{#1}{[xshift=\horizontalSpacing]#2.center}{#3}{#4}
    }

@@

@@

>>>>

\usepackage{longtable}
\usepackage[section]{placeins}
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
%\usepackage{hyperref}

@@

%\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{fit,bayesnet,calc,tikzmark}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{dsfont}
\usepackage{amsmath}

@@

Human knowledge, both in children and in adults, seems to be organized
into domains of expertise.  Some of us develop competence in cooking,
calculus, tennis, drawing pictures, or writing software, and virtually
every child masters natural language, motor control, and intuitive
theories of kinship, taxonomy, and physics. Over short timescales,
people can solve new problems within their domain of expertise, and
over longer time scales, they can grow into domain experts for 
new classes of problems.  A long-term goal for machine intelligence is
to build an AI that captures these two human abilities: both solving
new problems, and expanding the domains of problems that can be solved in
the first place.

We take the stance that an artificial agent with these humanlike
abilities needs at least two ingredients.  First it must acquire the
underlying system of domain-specific concepts.  For drawing pictures
these concepts include polygons, spirals, arcs, and symmetries; for
physics these concepts include dot products, vector fields, and
conservation laws.  Second it must learn to quickly deploy these
concepts efficiently on new problems: at a glance, human domain
experts can intuit which compositions of concepts are likely to solve
the task at hand, even before they begin searching for a solution.

We introduce a computational model that jointly acquires these two
kinds of domain knowledge.  Because solutions to many kinds of
problems can often be described as some kind of
program~\cite{lake2015human,Ullman2012,DBLP:journals/cogsr/SchmidK11},
our system solves a specific problem by searching for a program.  It
gradually grows its domain-specific knowledge for a class of problems
by assembling a library of code containing concepts useful for the
domain, and by training a neural network to quickly infer, for a
specific problem, what code concepts from its library are likely to
solve it.  We first investigate our model within classic program
synthesis domains for manipulating sequences of numbers and text, and
then consider visual and creative programs for drawing pictures and
building towers out of toy blocks, altogether considering both
deterministic and probabilistic programs that act both generatively
(e.g., producing an artifact like an image or plan) and conditionally
(e.g., mapping inputs to outputs).

We call our system `DreamCoder' because it works through a novel kind
of wake/sleep or `dream' learning~\cite{hinton1995wake}, iterating
through a wake cycle -- where it solves problems by writing programs
-- and a pair of sleep cycles, both of which are loosely biologically
inspired. The first sleep cycle, which we refer to as
\textbf{consolidation}, grows its library of code by replying
experiences from waking and consolidating them into new code
abstractions.  This cycle is inspired by the formation of abstractions
during sleep memory consolidation~\cite{DUDAI201520}.  The second
sleep cycle, which we refer to as \textbf{dreaming}, improves the
agents knowledge of how to write code by training a neural network to
help search for programs. The neural net is trained on replayed
experiences as well as `fantasies', or samples, from the learned
library.  These two kinds of dreams are inspired by the distinct
episodic replay and hallucination components of dream
sleep~\cite{fosse2003dreaming}.

\system builds on several generations of research in AI, program
synthesis, and cognitive science, with program induction being one of
the oldest theoretical frameworks for concept learning within
artificial intelligence~\cite{solomonoff1964formal}, and the
conceptually allied `Language of Thought Hypothesis' being almost as
old~\cite{fodor1975language}. Recent neural program synthesis systems
pair a fixed programming language to a learned neural network that
guides program
search~\cite{spiral,balog2016deepcoder,devlin2017neural}, while recent
symbolic AI research has developed frameworks for inferring 
reusable pieces of code shared in a multitask
setting~\cite{ecc,Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,DBLP:conf/ecai/LinDETM14}.
A main goal of this work is to combine and refine these techniques
with the intention of building agents that, like humans, develop
domain expertise for new classes of problems, motivated by models from
cognitive science that explain the flexibility and generality of human
thinking in terms of program-like mental representations, referred to
as a `language of thought'~\cite{piantadosi2011learning}.

Most prior program synthesis work assumes a fixed library of code
components~\cite{jha2010oracle} or a hand-engineered domain-specific
language (a `DSL'~\cite{polozov2015flashmeta,gulwani2011automating}).
In the vocabulary of program synthesis, our approach is to learn an
increasingly finely-tuned DSL (during consolidation) while jointly
learning to deploy it efficiently on new problems (during dreaming).
Each wake/sleep cycle creates new DSL components that build on
components learned in earlier sleep cycles, growing a DSL with nested
hierarchies of code.  We identify this cumulative nesting of
abstractions as a variety of deep representation
learning~\cite{lecun2015deep}.  Figure~\ref{exampleDSL} diagrams a
subset of these learned networks (the DSL). For example, the system
learns to sort sequences of numbers by invoking a DSL component 4
layers deep, or draws the leftmost pairs of images in
Figure~\ref{exampleDSL} using a depth-3 component.  For this reason we
refer to \system as an instance of `deep program learning'.

\section{Old introduction}

@@

    \newcommand{\invention}[4]{
      \node(#1)[inner sep=1,anchor=south,text width=2.2cm,ellipse,draw,rounded corners,align=center] at (#2) {
        \footnotesize #3
      };
      \node[anchor=north,align=center] at ([yshift=3.5pt]#1.south) {#4};
    }
    \newcommand{\vinvention}[4]{
      \invention{#1}{[yshift=-\verticalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\hinvention}[4]{
      \invention{#1}{[xshift=\horizontalSpacing]#2.south}{#3}{#4}
    }
    \newcommand{\exampleFunction}[2]{
      \includegraphics[width = 0.5cm]{#1}, \includegraphics[width = 0.5cm]{#2}
    }
    \newcommand{\task}[4]{
      \node[align=left,anchor=center](t#1) at (#2) {#3};
      \node[align=left](p#1) at ([yshift=-0.75cm]t#1.south) {#4};
    }
    \newcommand{\nextTask}[4]{
      \task{#1}{[xshift=\horizontalSpacing]#2.center}{#3}{#4}
    }

@@

\subsubsection{Generative Modeling of Text}
We investigate few-shot learning of generative models by tasking our
agent with inferring a probabilistic regular expression from a small
number (5) of strings - for example, observing the strings \$1.20 and \$9.42
and predicting the regex \$d

\begin{tabular}{ccc}
  \toprule   Observed text&Inferred regex&Held out testing text\\\midrule

  \end{tabular}

@@

\subsection{Results on held out text patterns}
%\makeatletter
\renewcommand{\verbatim@font}{\ttfamily\tiny} 
\input{regex.tex}
